---
title: "Visualize Emissions Scenarios"
date: "December 13, 2019" # update with new emissions factors
author: "Max Blasdel"
---

# Purpose
Visualize and analyze the totals csv output from running scenarios

```{r setup, message=FALSE}
library(tidyverse)
library(reshape2)
library(zoo)
library(magrittr)
library(wesanderson)

options(scipen = 20)
# this sets the wd to the project directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# Other funtions
Below script does not end up getting used

```{r}
source("scripts/constraint_factors.R") # this is not used anymore in this analysis

# capitalization function
simpleCap <- function(x) {
  s <- strsplit(x, " ")[[1]]
  paste(toupper(substring(s, 1,1)), substring(s, 2),
        sep="", collapse=" ")
}

```

# Totals data from scenarios

Load data

```{r}
tots <- dir("output/tabular/emissions/fuel_shift", pattern = ".csv", full.names = T)

csvs <- lapply(tots, function(x) {
  return(read.csv(x, stringsAsFactors = F))
})

tots <- do.call(rbind, csvs)
tots
```

Identify baseline values

This is a complicated way of reducing the number of baseline values as there are duplicates from each buffer distance

```{r}
base <-
  tots %>%
    filter(cook == 0 & water == 0 & space == 0 & lighting == 0) %>%
    group_by(region) %>%
    slice(1) %>%
    mutate(baseline = 1) %>%
    ungroup()

# filter out base case
tots <-
  tots %>%
  filter(cook != 0 | water != 0 | space != 0 | lighting != 0)

# chekc there are no other baseline scenarios
tots %>% 
  filter(baseline == 1)

# bind together and arrange
tots <-
  rbind(base, tots) %>%
  arrange(region)
```

Assign new variable based on scenarios calculated
*note* subject to change and addition

```{r}
tots <-
  tots %>% 
  mutate(scenario = case_when(baseline == 1 ~ "Baseline",
                              # dist == "buf_0km" ~ "Urban",
                              #cook == 1 & water == 1 & space == 1 ~ "Cooking, Water Heating, Space Heating",
                              cook == 1 & water == 0 & space == 0 & lighting == 0 ~ "Cooking",
                              cook == 0 & water == 1 & space == 0 & lighting == 0 ~ "Water Heating",
                              cook == 0 & water == 0 & space == 1 & lighting == 0 ~ "Space Heating",
                              cook == 0 & water == 0 & space == 0 & lighting == 1 ~ "Lighting",
                              cook == 1 & water == 1 & space == 1 & lighting == 1 ~ "All Services"),
        constrain = case_when(unconstrained == 1 ~ "Unconstrained",
                              unconstrained == 0 ~ "Constrained"),
        urban_rural = case_when(dist == "buf_0km" & scenario != "Baseline" ~ "Urban",
                                scenario == "Baseline" ~ "none",
                                T ~ "Rural")) %>% 
  # drop the indicator variables
  select(-c(cook, water, space, lighting, annual, urban, unconstrained, baseline))
```

Calculate percent reduction based on baseline

```{r}
tots <-
  tots %>%
  group_by(region) %>%
  # 1 minus calcs the percent reduction as opposed to percent of baseline
  mutate(percent_pm = 1 - pm_tot / first(pm_tot),
         percent_co2 = 1 - co2_tot / first(co2_tot),
         percent_bc = 1- bc_tot / first(bc_tot)) %>%
         ungroup()

# convert to factor for plotting
tots$dist <- tots$dist %>% factor(levels = tots$dist %>% unique(), ordered = T)

# make buf distance a numeric
tots$dist <- gsub("[^0-9]", "", tots$dist) %>% as.numeric()

# Prepare region names for graphing
tots %<>%
  mutate(region = gsub("_", " ", region))

# capitalize
tots$region <-
  sapply(tots$region, simpleCap)

# Get all regions in a list
region_list <- unique(tots[,"region"]) %>% 
  unlist()

# inspect
tots %>%
  head()
```

```{r}
max_height <-
  tots$percent_pm %>%
  max()
```


# Create plots (Deprecated)

## Particulate Matter
```{r}
# all_plots <-
#   lapply(region_list, function(g) {
# tots %>%
#   filter(region == g & scenario != "Baseline") %>% # filter for testing
#   ggplot() +
#   theme_minimal() +
#   geom_bar(aes(x = dist,
#                y = percent_pm,
#                fill = scenario),
#            stat = "identity") +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1),
#         legend.position = "bottom",
#         text = element_text(size = 16)) +
#   labs(y = bquote(bold("Percent Reduction from Baseline")),
#        title = "Change in Particulate Matter",
#        subtitle = g,
#        x = "Distance (km)",
#        color = "Fuel Scenarios") +
#   scale_x_continuous(breaks = seq(0,20,1)) +
#   scale_y_continuous(limits = c(0, max_height)) + # set the y scale
#   # geom_vline(xintercept = 0, # urban area shading
#   #            size = 10, 
#   #            alpha = .2) +
#   # geom_text(aes(x = 0, 
#   #               label = "Urban", # add urban designation
#   #               y = 0.5), # set text height
#   #           angle = 90) + # rotate horizontal
#   scale_fill_manual(values = wes_palette(n = 5, 
#                                          name = "Moonrise3")) + # color the legend
#   theme(legend.title = element_blank()) # remove legend
# })
# 
# all_plots
```

Save outputs
```{r}
# for (i in 1:length(region_list)) {
#   ggsave(paste0("../output/charts/fuels/bar/", region_list[i], ".png"), all_plots[[i]], dpi = 300, width = 7)
# }
```

reorder legend 
```{r}
tots$scenario <- factor(tots$scenario,
                        levels = c("Cooking",
                                   'Space Heating',
                                   "Water Heating", 
                                   'Lighting',
                                   "All Services"))
```

# Stacked area chart

```{r}
tots %>%
  filter(region == "Central" & scenario == "Water Heating")
```


```{r}
all_plots <-
   lapply(region_list, function(g) {
tots %>%
  filter(region == g & 
        !scenario %in% c("Baseline", "All Services") &
        constrain == "Unconstrained") %>% # filter for testing
  ggplot() +
  theme_minimal() +
  geom_area(aes(x = dist,
               y = percent_pm,
               fill = scenario),
           stat = "identity",
           position = position_stack(reverse = T)) +
  geom_line(data = filter(tots, constrain == "Constrained" & region == g & scenario == "All Services"),
                 aes(x = dist,
                     y = percent_pm),
            col = c("#00CD00"),
            lwd = 2,
            linetype = "dashed") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "bottom",
        text = element_text(size = 16)) +
  labs(y = bquote(bold("Percent Reduction from Baseline")),
       title = "Change in Particulate Matter",
       subtitle = g,
       x = "Distance (km)",
       color = "Fuel Scenarios") +
  scale_x_continuous(breaks = seq(0,20,1)) +
  scale_y_continuous(limits = c(0, max_height + .05)) + # set the y scale
  # geom_vline(xintercept = 0, # urban area shading
  #            size = 5, 
  #            alpha = .2) +
  # geom_text(aes(x = 0, 
  #               label = "Urban", # add urban designation
  #               y = 0.65), # set text height
  #           angle = 90) + # rotate horizontal
  scale_fill_manual(values = wes_palette(n = 4, # using fun wes anderson palette
                                         name = "GrandBudapest1")) + # color the legend
  theme(legend.title = element_blank()) # remove legend
 })

# test plot
all_plots
```

Save outputs for stacked area

```{r}
for (i in 1:length(region_list)) {
  ggsave(paste0("output/charts/fuels/stacked/", region_list[i], ".pdf"),
         all_plots[[i]],
         width = 12,
         height = 7,
         dpi = 500)
}
```

***
### Old workflow below this

# Show how constrain factor changes effected polygons

```{r}
census <- readRDS("../output/spatial/india_with_indicies.rds") %>% 
  as.data.frame()

# Replace NA values with preceding value
census$state_name <- na.locf(census$state_name)

state_designations <- read.csv("../sup_info/alt_zones.csv", stringsAsFactors = F) %>% 
  rename(zonal_council = zone)

# state_designations %<>% 
#   select(cID_1, zonal_council) %>% 
#   rename(STATE = cID_1)

#state_designations$zones <- gsub("_", " " , state_designations$zone)

dat <- inner_join(census, state_designations, by = c("STATE" = "state"))

dat %>% 
  count(zone)
```

## Prepare data (workflow moved tnetFunction())

This shows how many polygons are within the constrain factor that has been chosen.
```{r}
#zones <- dat$zonal_council %>% unique() %>% as.list()

# separate out different zonal council groups
#dat_zones <- split(dat, dat$zonal_council) # create list by region
```

Creating dataframe of values showing how constrain factor changes the effected polygons in different regions

Define variables for data processing
# NOTE moved to function; may be issues with capitalization of below code
```{r}
# # Set constrain values
# constrain_factor <- seq(0.01, 0.20, 0.01) %>% as.list()
# #### add in functionality to change constraint factor
# constraint <- 'maincook_lpg'
```

Calculate inclusion based on constraint factor
```{r}
# Created nested list for each factor and council zone
# effective_zones <- lapply(dat_zones, function(x) {
#   lapply(constrain_factor, function(y) {
#     x %>% 
#       transmute(eff = case_when(!!as.name(constraint) <= y ~ 0, # when the constraint is less than the constraint factor assign a 0, meaning the polygon is below a threshold and is not affected
#                               TRUE ~ 1) ) %>% 
#     count(eff) %>% # get number of polys meeting or not meeting requirement 
#     transmute(perc = n/sum(n)) # calculate as a percentage for each region and constraint factor
#   })
# })
```

Reformat data into more usable format
```{r}
# out <- sapply(effective_zones, simplify = F, USE.NAMES = T, function(x)  {
#  t <-  do.call(cbind, x) # combine all values into data.frame
#  colnames(t) <- constrain_factor
#   t <-  t[1,] %>% # take only the first value of percent affected
#     gather()
#  return(t)
# })
# 
# # bind rows and create new column based on list name ### SUPER USEFUL
# effective_zones <- bind_rows(out, .id = "Zone")
# 
# # make zones capital
# effective_zones$Zone <- sapply(effective_zones$Zone, simpleCap)
# 
# # Fix north east issue
# effective_zones$Zone <- gsub("North_east", "Northeast", effective_zones$Zone)
```

## Add in national level
```{r}
# #  run case when for all constrain factors
# all_constrain <- lapply(constrain_factor, function(x) {
#   dat %>%
#         transmute(eff = case_when(!!as.name(constraint) <= x ~ 0,
#                                 TRUE ~ 1) ) %>%
#       count(eff) %>%
#       transmute(perc = n/sum(n))
# })
# 
# all_constrain <- do.call(cbind, all_constrain)
# 
# # rename columns and rows
# colnames(all_constrain) <- constrain_factor
# rownames(all_constrain) <- c(1, 0)
# 
# # restructure df
# all_constrain <- all_constrain[1,] %>%
#   gather() %>%
#   mutate(zone = "national")
# 
# all_constrain$zone <- sapply(all_constrain$zone, simpleCap)
```

Create weighted average based on nPeople
```{r}
dat <- dat %>% 
  mutate(people_per_house = (1 * npersons_1) + 
                                   (2 * npersons_2) + 
                                   (3 * npersons_3) +
                                   (4 * npersons_4) +
                                   (5 * npersons_5) +
                                   (7 * npersons_6to8) +
                                   (10 * nperspns_gt9))
```


```{r}
dat$matroof_other
# some of the possible cut-offs
constraint = "people_per_house"
constraint = "literacy_rate"
constraint = "maincook_lpg"
constraint = "pop_density"
constraint = "quintiles"
constraint = "matroof_metal"
constraint = "matroof_plastic"
constraint = "matroof_concrete"
constraint = "nperspns_gt9"

ggplot(dat, aes(!!as.name(constraint))) +
    geom_histogram()

output_plotting <- constraintFunction(dataframe = dat, 
                           constraint = constraint, # constraint factor as string
#                           constraint_seq = seq(0,1,.05), 
                            constraint_seq = seq(2.5, 7.5, .5),
                          #constraint_seq = seq(1,5,1), # range of constraint factor
                           caps = T) # capitalize zones names, separate function
```

# plotting

```{r}
ggplot() +
  theme_minimal() +
  geom_line(data =  output_plotting %>% filter(zone != "National"),aes(as.numeric(key), value, color = zone, group = zone), size = 1.5) +
   geom_line(data = output_plotting %>% filter(zone == "National"), aes(as.numeric(key), value, group = zone, size = "National"), colour = "black") +
#  scale_y_continuous(limits = c(0, 1)) +
#  scale_x_continuous(limits = c(0, .1)) +
  guides(size = guide_legend(title = "Region")) + 
   labs(x = "Constraint Metric Value", 
       y = "Percent of Polygons Excluded",
       color = "Region", 
       title = "Changes Polygons Affected by Cutoff",
       subtitle = paste("Constraint Metric:", constraint)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#  geom_vline(xintercept =5, alpha = .7, color = "gray", size = 2)# + 
#  geom_point(aes(x = 5, y = .6716791), color = "red") 
```

# Save outputs
```{r}
ggsave(paste0("images/", constraint, ".png"), dpi = 400)

```


Change to population of regions for above graph
change scale of emissions graphs to numeric

4/3/19 Notes


Add forest areas to map of india, 

above graph for regions and national, line graph, work on wording
