---
author: 'Max Blasdel'
date: "7/17/2019"
---

# Purpose
This script will read in different data sources and join to the main shp file. 
The new data will be used as indicator variables for the fuel shift

```{r setup}
options(scipen = 20)
```

# load libraries

```{r message=FALSE}
library(sf)
library(dplyr)
library(ggplot2)
library(haven)
library(magrittr)
library(data.table)

source("../../scripts/polyCensusMerge.R")
```

The village level PCA census does not have literacy levels. It only has roof material, wall material, cooking preferences, etc. It appears to be more infrastructre based.

#### The census data contains a lot of the things we want for the indicator variable. Unfortunately I removed many of these columns in a later step to keep the column numbers low. I think it will be best to run through the original scripts again recreating the shapefile and not dropping the columns. This will allow me to clean things up and delete some of the multiple copies of the shp output file. 

## Outline w/ shapefile tracking
Task2 ---+ poly_census_merge.rmd
        merged_shp_w_fuelUseRasters_bilinear -> Shapefile_w_census
      
      ---+ remove_duplicate_data.rmd
        Shapefile_w_census -> poly_cen_update

Task3 
      ---+ Data Prep.rmd *This is the script that drops the columns I now need
        poly_update -> poly_update  
      
      ---+ EnergyToFuel_markdown.Rmd
        poly_update_RDS_cleaned.rds -> census_poly.rds
      
      ---+ fuelToEmissions_V2.rmd
        poly_cen.rds -> individual emissions files
      
      ## do not need the sum_* markdown
      ---+ sum_RowsTotalEnergy.rmd
        census_poly.rds -> poly_cen_colSums.rds 
      ---+ sum_TotalsEmissions.rmd
        poly_cen_colSums.rds -> total_species_emissions.rds
Task4
      ---+ urbanDistinctionChage.rmd #only run once to append data after 'create_spatial_buffers.rmd'
        poly_wScenarios_all.rds -> poly_wScenarios_all.rds # this is actually unneeded as it is a one line operation
    
      ---+ runScenarios.Rmd
        poly_wScenarios_all.rds -> outputs results

Task6 ---+ create_spatial_buffers.rmd
  poly_cleaned_w_tehsils.rds -> poly_w_all_scenarios.rds * this was run later to account for different buffer distances

# Load spatial data and inspect

This is the most recent sf file that is fed into the emissions scenarios scripts
```{r}
india <- read_rds("../../output/spatial/poly_w_all_buffers.rds")
```

# poly cen from poly_census_merge.rmd
# taking advantage of global environment, change at some point 

Work on dropping columns that are not needed
```{r}
poly_cen <- poly_cen %>% 
    filter(C_CODE0 %in% india$C_CODE0) # works but still need to merge onto india file

# maybe UID is a better choice
q <- poly_cen %>% 
  as.data.frame() %>% 
  select(C_CODE0,
         UID,
         matroof_burntBrick,
         matroof_plastic,
         matroof_handmadeTiles,
         matroof_manufacturedTiles,
         matroof_burntBrick,
         matroof_grassThatchBambWoodMud,
         matroof_slate,
         matroof_metal,
         matroof_concrete,
         matroof_other,
         nrooms_0,
         nrooms_1,
         nrooms_2,
         nrooms_3,
         nrooms_4,
         nrooms_5,
         nrooms_gt6,
         npersons_1,
         npersons_2,
         npersons_3,
         npersons_4,
         npersons_5,
         npersons_6to8,
         nperspns_gt9,
         literacy_rate,
      #   total,
         wquint_pca,
         wquint_pca_no_lpg,
         w_index_pca_score,
         w_index__pca_noplg_score,
         dsttownkm)


# try sorting data on join first
q <- q %>% arrange(C_CODE0)

# remove duplicates
q <- q %>% distinct()

india <- india %>% arrange(C_CODE0)

india <- left_join(india, q, by = c("C_CODE0" = "C_CODE0", "UID" = "UID" ))
```

Exploring other census information
* This gives:
  + Number of rooms 
  + Number of family members
  + Roof material

# Population density
Calculate population density

```{r}
india <- india %>% 
  mutate(pop_density = nPeople / area)

# returns some NA values for areas with 0 population. Turn these nas to 0
india <- india %>% 
  tidyr::replace_na(list(pop_density = 0))

india$pop_density %>% is.na() %>% sum()
```

Use MYID to remove extra rows.

Method with dplyr and averaging the extra rows together
## getting some nas for some reason
```{r}
india %<>% 
  as.data.frame() %>%
  group_by(MYID) %>% 
  mutate_at(.vars = vars(matroof_burntBrick,
         matroof_plastic,
         matroof_handmadeTiles,
         matroof_manufacturedTiles,
         matroof_burntBrick,
         matroof_grassThatchBambWoodMud,
         matroof_slate,
         matroof_metal,
         matroof_concrete,
         matroof_other,
         nrooms_0,
         nrooms_1,
         nrooms_2,
         nrooms_3,
         nrooms_4,
         nrooms_5,
         nrooms_gt6,
         npersons_1,
         npersons_2,
         npersons_3,
         npersons_4,
         npersons_5,
         npersons_6to8,
         nperspns_gt9,
         literacy_rate,
        # total,
        # quintiles,
         wquint_pca,
         wquint_pca_no_lpg,
         w_index_pca_score,
         w_index__pca_noplg_score,
         dsttownkm), .funs = mean) %>% 
  ungroup() %>% 
  distinct()
# 555,915 results
```

calculate a population per household metric here

```{r}
india <- india %>% 
  mutate(per_house_weighted = 
           (npersons_1 * 1) +
           (npersons_2 * 2) +
           (npersons_3 * 3) +
           (npersons_4 * 4) +
           (npersons_5 * 5) +
           (npersons_6to8 * 7) +
           (nperspns_gt9 * 9))
```

Check on urban rural maincook lpg usage
*needs work*

```{r}
india %>% 
  filter(grepl('Urban|Rural', TRU)) %>% 
  filter(as.numeric(pop_density) < 1.5) %>% 
ggplot() +
  theme_minimal() +
  geom_point(aes(x = as.numeric(pop_density), y = maincook_lpg, colour = TRU))
  # geom_smooth(aes(x = as.numeric(pop_density), y = maincook_lpg, colour = TRU)) +

india$pop_density %>% summary()
```

Write out version for Varun to use for correlation tests
```{r}
saveRDS(india, "../../output/spatial/india_with_indicies.rds")
```




