---
title: "Fix Census Variables"
date: "7/30/19"
author: "Max Blasdel"
---

# Purpose
There are 143 polygons that have percentages greater than 1 for the energy use variables. These polygons are the polygons that were identified with QGIS as missing from the dataset and individually exported from the original shapefile and added to the india sf file. Unfortunately this is the least well documented portion of this project and I am still looking for the code that performed the re-merge.
I am confident this is what caused the percentages to change by a factor of 100 as the numbers and names all match up with the shp files I have on disk. This script will change the percentages back to true percentages and export the resultant sf file.

# load packages

```{r}
library(dplyr)
```

# load data

```{r}
india <- readRDS("../../data/spatial/poly_w_all_buffers.rds")
getwd()
```

# subset data

```{r}
# seperate out large number areas
big_number_areas <- india %>% 
  as.data.frame() %>% 
  filter(maincook_lpg > 1 | maincook_wood > 1)

# change numbers to percentages for each category
big_number_areas <- 
  big_number_areas %>% 
  mutate_at(vars(contains("mainlight")), ~(./100)) %>% 
  mutate_at(vars(contains("maincook")), ~(./100)) %>% 
  mutate_at(vars(contains("latrines")), ~(./100)) %>% 
  mutate_at(vars(contains("cooklocation")), ~(./100))

big_number_areas$maincook_lpg
```


# merge back together

```{r}
india <- india %>% 
  filter(!MYID %in% big_number_areas$MYID)

# need to convert to data frame before spatial merge
india <- rbind(india %>% 
                 as.data.frame(), 
               big_number_areas)

india[is.na(india)] <-
  0
```

# Inspect

```{r}
india %>%
  pull(maincook_lpg) %>%
  summary()
```


```{r}
# convert back to sf object
india <- india %>% st_as_sf()
```

# save outputs

```{r}
saveRDS(india, "../../output/spatial/poly_w_all_buffers.rds")
```




