---
Title: "Task One for India Emissions"
Date: "November 18th 2018"
Author: "Max Blasdel"
---
# This script will be for merging the census data to the polygons shapefile of India
Load required packages
```{r message=FALSE}
library(dplyr) # main data manipulation
library(readr) # read csv functions
library(stringr) # string manipulation
#library(data.table)
library(sf) # manipulate spatial objects
library(magrittr) # use of %<>% operator
#library(sp) 
library(haven) # reads dta files
```

Read in the udir and rdir keys which link the census and the shapefiles. 
```{r}
# read in the urban dir file and create a new column of the census code number
udir <- read_dta("../../tabularData/census-link-files_census_2001-2011/udir.dta",encoding = "latin1")
udir %<>% mutate(code01_full = paste0(stc2001,dtc2001,subdt2001,plcn2001))
udir %<>% mutate(code11_full = paste0(mdds_stc, mdds_dtc, mdds_subdt, mdds_plcn))
udir$code01_full %<>% str_pad(width = 16,side = "right",pad="0")

rdir <- read_dta("../../tabularData/census-link-files_census_2001-2011/rdir.dta",encoding = "latin1")
rdir %<>% mutate(code01_full = paste0(stc2001,dtc2001,subdt2001,plcn2001))
rdir %<>% mutate(code11_full = paste0(mdds_stc, mdds_dtc, mdds_subdt, mdds_plcn))
rdir$code01_full %<>% str_pad(width = 16,side = "right",pad="0")
```

I want to drop some of the name columns here as well to reduce duplicates
```{r}
udir %<>% 
  select(-mdds_name)
rdir %<>% 
  select(-mdds_name)
```

# Census data
## Main census file

```{r}
#### upload merged data
pca_amen <- readRDS("../../tabularData/2011_villageTown_pcaAndAmenities/pcaAmen_2011_amenImputed")

# Need to rename these to reflect 2011 or 2001
pca_amen %<>% 
  mutate(code01_full.x = paste0(stc2001.x,dtc2001.x,subdt2001.x,plcn2001.x)) %>% #urban 2001
  mutate(code11_full.x = paste0(mdds_stc.x, mdds_dtc.x, mdds_subdt.x, mdds_plcn.x)) %>% #urban 2011 
  mutate(code01_full.y = paste0(stc2001.y, dtc2001.y, subdt2001.y, plcn2001.y)) %>% #rural 2001
  mutate(code11_full.y = paste0(mdds_stc.y, mdds_dtc.y, mdds_subdt.y, mdds_plcn.y)) #rural 2011
```
01 refers to 2001 and 11 refers to 2011. X is urban, Y is rural. 

*7/24/19*
## Literacy census file
Add in of join literacy rate census file

```{r}
lit_census <- read_csv("../../tabularData/pca_village.csv", col_types = cols()) %>% 
  select(State, District, Subdistt, `Town/Village`, Name, TOT_P, P_LIT) %>% 
  mutate(literacy_rate = P_LIT / TOT_P)

pca_amen <- left_join(pca_amen, lit_census, by = c("mdds_stc.y" = "State", 
                                       "mdds_dtc.y" = "District", 
                                       "mdds_subdt.y" = "Subdistt",
                                       "mdds_plcn.y" = "Town/Village"))
```

## wealth indices 
*also added on 7/24/19*
```{r}
# wealth <- read_csv("../../tabularData/wealthIndeces/processed/wealth_quintiles.csv", col_types = cols()) %>% 
#   select(state_code, district_code, subdistrict_code, village_code, total, quintiles)
# 
# # pad with zeros
# wealth$state_code %<>% str_pad(width = 2, side = "left", pad = 0)
# wealth$district_code %<>% str_pad(width = 3, side = "left", pad = 0)
# wealth$subdistrict_code %<>% str_pad(width = 5, side = "left", pad = 0)
# wealth$village_code %<>% str_pad(width = 6, side = "left", pad = 0)
# 
# pca_amen <- left_join(pca_amen, wealth, by = c("mdds_stc.y" = "state_code", 
#                                        "mdds_dtc.y" = "district_code", 
#                                        "mdds_subdt.y" = "subdistrict_code",
#                                        "mdds_plcn.y" = "village_code"))


wealth <- read.csv("../../wealth_q_pca/wealth_quintiles_pca_01152020_VG.csv")

# pad with zeros
wealth$state_code %<>% str_pad(width = 2, side = "left", pad = 0)
wealth$district_code %<>% str_pad(width = 3, side = "left", pad = 0)
wealth$subdistrict_code %<>% str_pad(width = 5, side = "left", pad = 0)
wealth$village_code %<>% str_pad(width = 6, side = "left", pad = 0)

pca_amen <- left_join(pca_amen, wealth, by = c("mdds_stc.y" = "state_code", 
                                       "mdds_dtc.y" = "district_code", 
                                       "mdds_subdt.y" = "subdistrict_code",
                                       "mdds_plcn.y" = "village_code"))
```

## distance to town 
*added on 8/6/19* follows same merge pattern as previous datasets
```{r}
distance <- read_csv("../../tabularData/2011_villageDirectory/village_directory_2011wcode_modSmall.csv", col_types = cols()) %>% 
  select(statcode,
         distcode, 
         sdiscode, 
         villcode,
         dsttownkm)

distance$statcode %<>% str_pad(width = 2, side = "left", pad = 0)
distance$distcode %<>% str_pad(width = 3, side = "left", pad = 0)
distance$sdiscode %<>% str_pad(width = 5, side = "left", pad = 0)
distance$villcode %<>% str_pad(width = 6, side = "left", pad = 0)

pca_amen <- left_join(pca_amen, distance, by = c("mdds_stc.y" = "statcode", 
                                       "mdds_dtc.y" = "distcode", 
                                       "mdds_subdt.y" = "sdiscode",
                                       "mdds_plcn.y" = "villcode"))
```


I want to drop some of the name columns because it was found that they cause duplicates later on.

```{r}
pca_amen %<>% 
  select(-name, -mdds_name.x)
```


Some of the code01 values are not 16 digits long and seem to be missing values on the right or place section. This can be padded with 0s but I do not think this will result in any matches with the polygons.
merging the udir/rdir and the pca
This step connects the udir and census data, this produces more matches with the polygons

```{r}
# Urban 2011 census with udir 2011 code
udir_merge<- inner_join(udir, pca_amen, by=c("code11_full"="code11_full.x"))
# Rural 2011 census with rdir 2011 code
rdir_merge<- inner_join(rdir, pca_amen, by=c("code11_full"="code11_full.y"))
rm(udir, rdir)
```

*2/7/19* Update with new shapefile from Varun. Issues with which RDS to use.
Read in polygon file. Using shapefile as opposed to RDS.
```{r add shapefile data}
# Compressed RDS version
merged_shp <- readRDS("../../geoData/fuelEndUses/merged_shp_w_fuelUseRasters_bilinear")
merged_shp %<>% st_as_sf()
```

Joining the udir_merge with the polygon on the 2001 codes. This should result in polygons with 
*With full dataset; examine the TRU=NA returns for each join. Look into population numbers*

```{r}
urb_cen <- inner_join(merged_shp, udir_merge, by=c("C_CODE01"="code01_full")) #4,798
rur_cen <- inner_join(merged_shp, rdir_merge, by=c("C_CODE01"="code01_full")) #612,329

# Just a check for merging on code11. Joining on the 2011 code produces nothing
# inner_join(merged_shp, udir_merge, by=c("C_CODE01"="code11_full.y"))
# udir_merge[,115:120] %>% head()
```

Explore some of the population numbers.
```{r}
#poly_cen<-rbind(urb_cen, rur_cen) # Doesn't work because some of the rows are different. Due to how they were merge. These fields are not needed and will be dropped.
urb_cen[,176:177]<-NULL
rur_cen[,176:177]<-NULL

# final polygon wil be written out later on
poly_cen <- rbind(urb_cen, rur_cen)
```

Remove un-needed items

```{r}
rm(merged_shp, udir_merge, rdir_merge, pca_amen, rur_cen, urb_cen, wealth, distance, lit_census)
gc()
```

Rename variable for simplicity

```{r}
poly_cen <- poly_cen %>% 
  rename(C_CODE0 = C_CODE01)
```

*7/18/19* In a quest to add census information in the least painless way I am just taking the global var poly_cen and moving to the add_census_data.rmd for further processing

Write the resultant shapefile or the data.frame without the geometry

```{r}
saveRDS(poly_cen, "../output/spatial/Shapefile_w_census.RDS")
```
