---
Title: "Looking into Odisha, State 21"
Date: "Dec 23, 2018"
---

#For Exploring some of the census data connected to Odisha
Inputs: original data
Outputs: none

```{r message=FALSE}
require(tidyverse)
require(sf)
require(magrittr)
```

Read in the census information
```{r}
pca_amen <- readRDS("../census/pcaAmen_2011_amenImputed")
poly_cen<-read_rds("Shapefile_w_census") %>% st_as_sf()
```

Isolate Odisha in the census information and the polygon.
Calculate some population numbers.
```{r}
Odisha_poly<-poly_cen %>% 
  filter(state_name == "ODISHA")

Odisha<-pca_amen %>% 
  filter(state_name == "ODISHA")

data.frame("Odisha Poly" = Odisha_poly$nPeople %>% sum(),
           "Odisha Census" = Odisha$nPeople %>% sum(),
           "Difference" = Odisha$nPeople %>% sum() - Odisha_poly$nPeople %>% sum())
rm(pca_amen, poly_cen)
```
There is a difference of about 7.8M people

```{r}
Odisha$urbanRural.y %>% unique() # only returns urban and rural
Odisha$level %>% unique() # only village or town
```


Find the number of unique identifiers that get used in the spatial merge
```{r}
rur_plcn<- Odisha$mdds_plcn.y %>% unique() %>% length() # codes to Rural
urb_plcn<- Odisha$mdds_plcn.x %>% unique() %>% length() # codes to Urban
rur_plcn+urb_plcn # sums to 47923, 16 off the total number

# Find the identifier codes that occur more than once for rur and urb
rur_plcn<-Odisha$mdds_plcn.y %>%
  table() %>% 
  data.frame() %>% 
  filter(Freq > 1)

urb_plcn<-Odisha$mdds_plcn.x %>% 
  table() %>% 
  data.frame() %>%
  filter(Freq > 1)
```

Finds the duplicate indentifier values.
Reduces to just first row
```{r}
rur<-list()
for (i in 1:nrow(rur_plcn)){
temp<-rur_plcn$.[i] %>% as.character() %>% as.numeric() # is in factor, convert
temp<-Odisha %>% # filter based on codes with doubles
  filter(mdds_plcn.y == temp)
rur[[i]]<-temp[1,] # Take just one row from these duplicates
}

urb<-list() # repeat for urban
for (i in 1:nrow(urb_plcn)){
  temp <- urb_plcn$.[i] %>% as.character() %>% as.numeric()
  temp<-Odisha %>% 
    filter(mdds_plcn.x == temp)
  urb[[i]]<-temp[1,]
}
```

Bind results together and then update original db
```{r}
uniqs<-rbind(do.call(rbind, rur), do.call(rbind, urb))

# Construct some simple dataframes of the plcn codes that need to be removed from the Odisha df
r<-rur_plcn$. %>% as.data.frame() %>% #Seperate out the plcn codes from rural
  rename(mdds_plcn.y = '.')
r<-transform(r, mdds_plcn.y = as.character(mdds_plcn.y))

u<-urb_plcn$. %>% as.data.frame() %>% 
  rename(mdds_plcn.x = '.')
u<-transform(u, mdds_plcn.x = as.character(mdds_plcn.x)) 

# Run the antijoins seperately
Odisha_unique<-anti_join(Odisha, r)
Odisha_unique<-anti_join(Odisha_unique, u)
#Bind together
# Bind the unique values back into the Odisha census information
Odisha_update<-rbind(Odisha_unique, uniqs)

# Look at changes in population
data.frame("Odisha Poly" = Odisha_poly$nPeople %>% sum(),
           "Odisha Census" = Odisha$nPeople %>% sum(),
           "Difference" = Odisha$nPeople %>% sum() - Odisha_poly$nPeople %>% sum(),
           "Odisha wo Duplicates" = Odisha_update$nPeople %>% sum())

Odisha_unique$nPeople %>% sum()
```

Removing the duplicate entries from the census removed about 4.5M people from the count. These duplicates are due to slight differences in names and some of the plcn codes. It appears that duplicates are caused by differences in how the names are recorded. 
```{r}
  temp <- urb_plcn$.[1] %>% as.character() %>% as.numeric()
  temp<-Odisha %>% 
    filter(mdds_plcn.x == temp)
  temp # scroll to the mdds_name.x
```

Remove junk

```{r}
rm(urb, urb_plcn, rur, rur_plcn, r, u, uniqs)
gc()
```

# Explore Odisha some more

Try to quantify the NA values in the Odisha census information
```{r}
Odisha %>% head()
```

I want to look at how the polygon and the census informatino differ. What are some Of the entries that are not connected to the census.

Prepare the census information with the process from Task 1
```{r}
Odisha_unique %<>% 
  mutate(code01_full.x = paste0(stc2001.x,dtc2001.x,subdt2001.x,plcn2001.x)) %>% #urban 2001
  mutate(code11_full.x = paste0(mdds_stc.x, mdds_dtc.x, mdds_subdt.x, mdds_plcn.x)) %>% #urban 2011 
  mutate(code01_full.y = paste0(stc2001.y, dtc2001.y, subdt2001.y, plcn2001.y)) %>% #rural 2001
  mutate(code11_full.y = paste0(mdds_stc.y, mdds_dtc.y, mdds_subdt.y, mdds_plcn.y)) #rural 2011
```

trying to anti join to find data that is in the census but not the polygon.
```{r}
anti_join(Odisha, Odisha_poly, by=c("code01_full.y" = "C_CODE0"))
anti_join(Odisha, Odisha_poly, by=c("code01_full.x" = "C_CODE0"))
```
Trying to just use single columns see if numbers differ
```{r}
code01_full.y<-Odisha_unique$code01_full.y %>% as.data.frame()
code01_full.x<-Odisha_unique$code01_full.x %>% as.data.frame()
CCODE_0<-Odisha_poly$C_CODE0 %>% as.data.frame()

anti_join(code01_full.y, CCODE_0)
anti_join(code01_full.x, CCODE_0)

```




```{r}
# plcn_rur<-Odisha_poly$mdds_plcn.y %>% na.omit()
# plcn_rur %<>% as.data.frame() %>% rename(mdds_plcn.y = '.')
# 
# plcn_rur<-transform(plcn_rur, mdds_plcn.y = mdds_plcn.y %>% as.character())

# Remove the spatial attributes for easier data merging
st_geometry(Odisha_poly)<-NULL
Odisha_poly

Lost_census_info.y<-anti_join(Odisha_unique, Odisha_poly, by = "plcn2001.y")
Lost_census_info.x<-anti_join(Odisha_unique, Odisha_poly, by = "plcn2001.x")
```

Explore the lost census information
*confusing*
Numbers don't add up correctly

```{r}
Lost_census_info.y$nPeople %>% sum()
Lost_census_info.x$nPeople %>% sum()
```

